### 2014-07-09 Paper_v1.tex
going home ...

In this study, we present an effective cell free metabolic modeling framework, and test this framework using two proof of concept metabolic models. 
[FINISH].

@@

\section*{Discussion}
In this study, we proposed a dynamic modeling strategy to simulate cell free metabolic networks. We demonstrated this strategy using two proof of concept metabolic networks 
with the same enzymatic connectivity, but differing control structures. [FINISH]

>>>>

In this study, we present an effective cell free metabolic modeling framework, and test this framework using two proof of concept metabolic networks. 
[FINISH].

@@

\section*{Discussion}
In this study, we proposed a effective modeling strategy to simulate cell free metabolic networks. 
We tested this strategy using two proof of concept metabolic networks 
with the same enzymatic connectivity, but differing control structures. [FINISH]
